DATA 621---Business Analytics and Data Mining

### 2020-09-18 HW1/HW1_draft_kellogg.Rmd
ambers final edits

We can see off the bat that a few variables *exceed* the 0.05 p-value threshold for 
significance: `TEAM_BATTING_H`, `TEAM_PITCHING_H` and `TEAM_PITCHING_BB`. Additionally, 
we see that both `TEAM_BATTING_1B` and `AB` have no coefficients at all! This is likely 
due to the fact that they are colinear with other variables in the model.

@@

Fielding double plays and batting doubles both appear to have negative impacts
on wins even though they *should* be positive impacts. Turning double plays,
while a good for the defensive team, may suggest a larger, negative issue.
Namely, weak pitching that leads to runners on base. Similarly, batting doubles,
leaves runners open to double plays. Allowed hits by pitching, caught stealing,
and batting strike-outs are all counter intuitive results as well, but they seem
to be small contributors and these are events that happen regularly in every
game.

>>>>

We can see off the bat that a few variables *exceed* the 0.05 p-value threshold for 
significance. Additionally, we see that both `TEAM_BATTING_1B` and `AB` have no 
coefficients at all! This is likely due to the fact that they are colinear with other 
variables in the model.

@@

First, we see that the intercept itself is negative. This means that, given no information
about any of the statistics, we would predict that a team would lose (by a lot!).

Next, fielding double plays and batting doubles both appear to have negative impacts
on wins even though they *should* be positive impacts. Turning double plays,
while a good for the defensive team, may suggest a larger, negative issue.
Namely, weak pitching that leads to runners on base. Similarly, batting doubles,
leaves runners open to double plays. Allowed hits by pitching, caught stealing,
and batting strike-outs are all counter intuitive results as well, but they seem
to be small contributors and these are events that happen regularly in every
game.
